08-prediction

### 2018-11-28 02_scripts/version-1/035-all-plots-modeling.Rmd
save state

```{r}
m = readRDS("/data/patrick/mod/hyperspectral/prediction/xgboost_trained_tuned.rda")
# 5h 30 min
var_imp = generateFeatureImportanceData(task, learner = lrn_xgboost, 
                                        measure = rmse, nmc = 50)
saveRDS(var_imp, "/data/patrick/mod/hyperspectral/variable-importance/bf2_ncm50rda")

@@

```{r}
imp.xgb = getFeatureImportance(m) 
imp.xgb$res = tidyr::gather(imp.xgb$res, "index", "feat.imp")

@@

```{r}
X = task$env$data[which(names(task$env$data) != "defoliation")]
predictor = Predictor$new(m, data = X, y = task$env$data$defoliation)
imp = FeatureImp$new(predictor, loss = "rmse")
```

@@

>>>>

```{r}
# 5h 30 min with 2 nmc
var_imp = generateFeatureImportanceData(task, learner = lrn_xgboost, 
                                        measure = rmse, nmc = 50)
var_imp = readRDS("/data/patrick/mod/hyperspectral/variable-importance/bf2_ncm50rda")

@@

```{r}
m = readRDS("/data/patrick/mod/hyperspectral/prediction/xgboost_trained_tuned.rda")
imp.xgb = getFeatureImportance(m) 
imp.xgb$res = tidyr::gather(imp.xgb$res, "index", "feat.imp")

@@

```{r}
model_xgboost_defol = readRDS("/data/patrick/mod/hyperspectral/prediction/xgboost_trained_tuned.rda")
library("doParallel")
cl = makePSOCKcluster(40)
# Registers cluster
registerDoParallel(cl)

X = task$env$data[which(names(task$env$data) != "defoliation")]

# correct column order of features: https://github.com/dmlc/xgboost/issues/1809
X = X[model_xgboost_defol$learner.model$feature_names]

predictor = Predictor$new(model_xgboost_defol, data = X, y = task$env$data$defoliation)
imp = FeatureImp$new(predictor, loss = "rmse", parallel = TRUE, n.repetitions = 100)
stopCluster(cl)
saveRDS(imp, "/data/patrick/mod/hyperspectral/variable-importance/feature-imp-iml.rda")

imp = readRDS("/data/patrick/mod/hyperspectral/variable-importance/feature-imp-iml.rda")
```

@@

## xgboost feat sel and tune

```{r}
lrn_xgboost = makeFilterWrapper(learner = lrn_xgboost,
                                imp.learner = c("regr.xgboost"))
```

```{r}
ps_xgboost_mrmr <- makeParamSet(
  makeIntegerParam("nrounds", lower = 10, upper = 600),
  makeNumericParam("colsample_bytree", lower = 0.3, upper = 0.7),
  makeNumericParam("subsample", lower = 0.25, upper = 1),
  makeIntegerParam("max_depth", lower = 1, upper = 10),
  makeNumericParam("gamma", lower = 0, upper = 10),
  makeNumericParam("eta", lower = 0.001, upper = 0.6),
  makeNumericParam("min_child_weight", lower = 0, upper = 20),
  makeDiscreteParam("fw.method", "mrmr"),
  makeNumericParam("fw.perc", lower = 0, upper = 1)
)

ps_xgboost_permut <- makeParamSet(
  makeIntegerParam("nrounds", lower = 10, upper = 600),
  makeNumericParam("colsample_bytree", lower = 0.3, upper = 0.7),
  makeNumericParam("subsample", lower = 0.25, upper = 1),
  makeIntegerParam("max_depth", lower = 1, upper = 10),
  makeNumericParam("gamma", lower = 0, upper = 10),
  makeNumericParam("eta", lower = 0.001, upper = 0.6),
  makeNumericParam("min_child_weight", lower = 0, upper = 20),
  makeDiscreteParam("fw.method", "permutation.importance"),
  makeNumericParam("fw.perc", lower = 0, upper = 1)
)
```

### tune wrapper

```{r}
tune_wrapper_mrmr <- makeTuneWrapper(lrn_xgboost, resampling = inner, 
                                     par.set = ps_xgboost_mrmr,
                                     control = tune.ctrl, show.info = TRUE,
                                     measures = list(rmse))
tune_wrapper_permut <- makeTuneWrapper(lrn_xgboost, resampling = inner, 
                                       par.set = ps_xgboost_permut,
                                       control = tune.ctrl, show.info = TRUE,
                                       measures = list(rmse))
```

### Resample

```{r}
library(parallelMap)
parallelStart(mode = "multicore", cpus = 30, level = "mlrMBO.feval",
              mc.set.seed = TRUE)
# parallelStart(mode = "multicore", cpus = 4, level = "mlr.resample",
#               mc.set.seed = TRUE)
set.seed(12345)
resa_svm <- mlr::resample(tune_wrapper, task, models = FALSE,
                          resampling = outer, 
                          extract = function(x) list(getFeatSelResult, getTuneResult),
                          show.info = TRUE, measures = list(rmse))

benchm <- benchmark(tune_wrapper, task, models = FALSE,
                          resampling = outer, 
                          extract = function(x) list(getFeatSelResult, getTuneResult),
                          show.info = TRUE, measures = list(rmse))

parallelStop()
saveRDS(resa_svm, "/data/patrick/mod/hyperspectral/spcv/all_plots_xgboost_fs_tune.rda")
```

### 2018-11-28 02_scripts/version-1/07_benchmark_all_plots.Rmd
save state

# XGBOOST
ps_xgboost <- makeParamSet(
  makeDiscreteParam("nrounds", values = c(10, 100, 1000, 10000)),
  makeNumericParam("colsample_bytree", lower = 0.1, upper = 1),
  makeNumericParam("subsample", lower = 0.1, upper = 1),
  makeIntegerParam("max_depth", lower = 1, upper = 785),
  makeNumericParam("gamma", lower = 0, upper = 20)
)
tune.ctrl <- makeTuneControlMBO(
  mbo.control = ctrl,
  mbo.design = generateDesign(n = 30, par.set = ps_xgboost)
)
tune_wrapper_xgboost <- makeTuneWrapper(makeLearner("regr.xgboost",
                                                    par.vals = list(
                                                      objective = "reg:linear",
                                                      eval_metric = "error",
                                                      eta = 0.1
                                                    )
),
resampling = inner, par.set = ps_xgboost,
control = tune.ctrl, show.info = TRUE,
measures = list(rmse)
)

# RF
ps_rf <- makeParamSet(
  makeIntegerParam("mtry", lower = 1, upper = 7000),
  makeIntegerParam("min.node.size", lower = 1, upper = 10),
  makeNumericParam("sample.fraction", lower = 0.2, upper = 0.9)
)
tune.ctrl <- makeTuneControlMBO(
  mbo.control = ctrl,
  mbo.design = generateDesign(n = 30, par.set = ps_rf)
)
tune_wrapper_rf <- makeTuneWrapper(makeLearner("classif.ranger"),
                                   resampling = inner, par.set = ps_rf,
                                   control = tune.ctrl, show.info = TRUE,
                                   measures = list(rmse)
)

>>>>

# XGBOOST
ps_xgboost <- makeParamSet(
  makeNumericParam("nrounds", lower = 0, upper = 8.64, 
                   trafo = function (x) round(2^x * 10)),
  makeNumericParam("colsample_bytree", lower = 0.3, upper = 0.7),
  makeNumericParam("subsample", lower = 0.25, upper = 1),
  makeIntegerParam("max_depth", lower = 1, upper = 10),
  makeNumericParam("gamma", lower = 0, upper = 10),
  makeNumericParam("eta", lower = 0.001, upper = 0.6),
  makeNumericParam("min_child_weight", lower = 0, upper = 20)
)
tune.ctrl <- makeTuneControlMBO(
  mbo.control = ctrl,
  mbo.design = generateDesign(n = 30, par.set = ps_xgboost)
)
tune_wrapper_xgboost <- makeTuneWrapper(makeLearner("regr.xgboost",
                                                    par.vals = list(
                                                      objective = "reg:linear",
                                                      eval_metric = "error"
                                                    )
),
resampling = inner, par.set = ps_xgboost,
control = tune.ctrl, show.info = TRUE,
measures = list(rmse)
)

# RF
ps_rf <- makeParamSet(
  makeIntegerParam("mtry", lower = 1, upper = 7000),
  makeIntegerParam("min.node.size", lower = 1, upper = 10),
  makeNumericParam("sample.fraction", lower = 0.2, upper = 0.9)
)
tune.ctrl <- makeTuneControlMBO(
  mbo.control = ctrl,
  mbo.design = generateDesign(n = 30, par.set = ps_rf)
)
tune_wrapper_rf <- makeTuneWrapper(makeLearner("regr.ranger"),
                                   resampling = inner, par.set = ps_rf,
                                   control = tune.ctrl, show.info = TRUE,
                                   measures = list(rmse)
)

### 2018-11-28 02_scripts/version-1/08_prediction.Rmd
save state

```{r}
# lattice.options(
#   layout.heights=list(bottom.padding=list(x=0), top.padding=list(x=0)),
#   layout.widths=list(left.padding=list(x=0), right.padding=list(x=0))
# )

raster_list_wgs84 = map(raster_list, ~ projectRaster(.x, crs = "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))

@@

```{r}
png("../03_figures/results/predictions_demon_plots.png", units = "in", width = 13, height = 9.21, res = 300)
gridExtra::grid.arrange(grobs = maps, nrow = 2, ncol = 2)
dev.off()

@@

>>>>

```{r}
raster_list_wgs84 = map(raster_list, ~ projectRaster(.x, crs = "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))

@@

```{r}
png("../03_figures/results/predictions_demon_plots.png", units = "in", width = 13, height = 9.21, res = 300)
gridExtra::grid.arrange(grobs = maps, nrow = 2, ncol = 2)
dev.off()
```

@@

# Plot all plots

```{r}
raster_list = map(list.files("/data/patrick/mod/hyperspectral/prediction/", 
                             pattern = "defol-pred*", full.names = TRUE), 
                  ~ raster(.x)
                  )
raster_list_wgs84 = map(raster_list, 
                        ~ projectRaster(.x, crs = "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")) %>% 
  map(~ set_names(.x, "defoliation"))

name = c("Aguinaga", "Altube", "Azaceta", "Barazar", "busturi", "Caranca",
         "Douglas 1", "Douglas 2", "Douglas Albiztur", "Douglas Legutio",
         "Gipuzkoa", "Laricio Defol Olaeta", "Laricio Defol Urkiola",
         "Laricio Gatzaga", "Laukiz 1", "Laukiz 2", "Laukiz 3", "Luiando", 
         "Oiartzun", "Oxtandio", "Picea Abornicano", "Pinas Santa Koloma",
         "Pinast Arza", "Rad Altube", "Rad Menagaray", "Sequoia Legorreta", 
         "Silvest Nograro")

maps = imap(raster_list_wgs84, ~ levelplot( 
  .x[["defoliation"]], 
  main = glue::glue("{tools::toTitleCase(name[.y])}: Defoliation [%]"), 
  #main = glue::glue("{tools::toTitleCase(.y)}"), 
  margin = FALSE,                             
  between = list(x = 0.0, y = 0.0), 
  at = seq(30, 82, length.out = 100), # min/max from map(raster_list_wgs84, ~ summary(.x))
  colorkey = list(
    width = 0.75,                       
    space = 'right',  
    labels = list(#at = c(0, 25, 50, 75, 100),
                font = 4),      
    axis.line = list(col = 'black')
  ),
  par.strip.text = list(col = "white", cex = 1.2),    
  col.regions = viridis)    
)
```

```{r}
png("../03_figures/results/predictions_plots-1-4.png", units = "in", 
    width = 13, height = 9.21, res = 300)
gridExtra::grid.arrange(grobs = maps[1:4], nrow = 2, ncol = 2)
dev.off()

png("../03_figures/results/predictions_plots-5-8.png", units = "in", 
    width = 13, height = 9.21, res = 300)
gridExtra::grid.arrange(grobs = maps[5:8], nrow = 2, ncol = 2)
dev.off()

png("../03_figures/results/predictions_plots-9-12.png", units = "in", 
    width = 13, height = 9.21, res = 300)
gridExtra::grid.arrange(grobs = maps[9:12], nrow = 2, ncol = 2)
dev.off()

png("../03_figures/results/predictions_plots-12-16-.png", units = "in", 
    width = 13, height = 9.21, res = 300)
gridExtra::grid.arrange(grobs = maps[13:16], nrow = 2, ncol = 2)
dev.off()

png("../03_figures/results/predictions_plots-17-20.png", units = "in", 
    width = 13, height = 9.21, res = 300)
gridExtra::grid.arrange(grobs = maps[17:20], nrow = 2, ncol = 2)
dev.off()

png("../03_figures/results/predictions_plots-21-24.png", units = "in", 
    width = 13, height = 9.21, res = 300)
gridExtra::grid.arrange(grobs = maps[21:24], nrow = 2, ncol = 2)
dev.off()

png("../03_figures/results/predictions_plots-25-28.png", units = "in", 
    width = 13, height = 9.21, res = 300)
gridExtra::grid.arrange(grobs = maps[25:28], nrow = 2, ncol = 2)
dev.off()
```
